Continous time Markov chain models; \\ extension, simulation and visualisation

### 2014-11-17 frontback/summary.tex
eerste edits samenvatting
more edits samenvatting

\emph{``28 grams of prevention are worth 454 grams of cure''}
--- An old saying

@@

Emergence of pandemic outbreaks, which we witness with alarmingly increasing frequency, represents a clear and imminent threat to the public health. 
This threat has been exemplified by the H1N1 influenza A outbreak, or the Ebola virus outbreak in West Africa.
Combating viral spread and their associated disease burden is a tremendous challenge requiring significant research efforts and decided public health measures.

Viral sequence data, which is now becoming available in unprecedented quantities and with remarkable rapidity, is frequently characterized to be one of the main assets in characterization of pathogens associated with high mortality. 
The research direction coined `phylodynamics' integrates molecular and epidemiological data, aiming to develop a full quantitative understanding  of the processes that shape the epidemiology, evolution and spread of viruses.

In this thesis I outline my contributions to pursue comprehensive analyses of the interaction between the ecological and evolutionary dynamics of emerging viruses.
In particular this PhD project aims at advancing statistical models for unravelling viral spatiotemporal history, to provide adequate visualization of our statistical estimates, and to alleviate the computational burden associated with drawing inference under these models.

I believe that these developments will ultimately contribute to the development of effective intervention and prevention strategies.

>>>>

\emph{`An ounce of prevention is worth a pound  of cure'}
--- An old saying

@@

The emergence of pandemic outbreaks, which we witness with an alarmingly increasing frequency, represent a clear and imminent threat to the public health. 
This threat has been exemplified by the H1N1 influenza A outbreak in 2009 or the Ebola virus outbreak in West Africa in 2014.
Combating viral spread and their associated disease burden is a tremendous challenge requiring significant research efforts and decided public health measures.

Viral sequence data, which is now becoming available in unprecedented quantities and with remarkable rapidity, is frequently considered to be one of the main assets in the characterization of pathogens associated with high mortality. 
The research direction coined `phylodynamics' integrates molecular and epidemiological data and aims to develop a full quantitative understanding  of the processes that shape the epidemiology, evolution and spread of viruses.

In this thesis I outline my contributions to pursue comprehensive analyses of the interaction between the ecological and evolutionary dynamics of emerging viruses.
In particular this PhD project aims at advancing statistical models for unravelling viral spatiotemporal history, to provide adequate visualization of our statistical estimates, and to alleviate the computational burden associated with drawing inference under these models.
I believe that these developments have the potential to results in a better understanding of pathogen epidemiology and evolution, which may ultimately assist in designing effective intervention and prevention strategies.
